Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-02-06 _paper.rmd
installation

The following __R__ code will help with getting up and running:

```{r eval=FALSE, echo=TRUE}
## Download the package
install.packages("cheem", dependencies = TRUE)
## Restart the R session, so the IDE has the correct directory structure
restartSession()
## Load cheem into session
library("cheem")
## Try the app
run_app()

# Processing your data
## Install treeshap from github to use as a local explainer
remotes::install_github('ModelOriented/treeshap')
## Follow the examples in cheem_ls()
?cheem_ls
```

>>>>

The package can be installed from GitHub using the following __R__ code:

```{r eval=FALSE, echo=TRUE}
# install.packages("remotes") # if you don't have it
remotes::install.packages("cheem", dependencies = TRUE)
library("cheem")
run_app()
```

To process your own data, you will need to use the `treeshap` package, which can be installed from GitHub:

```{r eval=FALSE, echo=TRUE}
remotes::install_github('ModelOriented/treeshap')
```

and follow the examples provided with the package to compute the local explainers. XXX Add some information on what type of data object gets passed into cheem.

Alternatively, the cheem viewer shiny app can be directly accessed at https://ebsmonash.shinyapps.io/cheem_initial/.

### 2022-02-06 _paper.tex
installation

The following \textbf{R} code will help with getting up and running:

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# Download the package}
\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\DocumentationTok{\#\# Restart the R session, so the IDE has the correct directory structure}
\FunctionTok{restartSession}\NormalTok{()}
\DocumentationTok{\#\# Load cheem into session}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\DocumentationTok{\#\# Try the app}
\FunctionTok{run\_app}\NormalTok{()}

\CommentTok{\# Processing your data}
\DocumentationTok{\#\# Install treeshap from github to use as a local explainer}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\DocumentationTok{\#\# Follow the examples in cheem\_ls()}
\NormalTok{?cheem\_ls}
\end{Highlighting}
\end{Shaded}

>>>>

The package can be installed from GitHub using the following \textbf{R} code:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# install.packages("remotes") \# if you don\textquotesingle{}t have it}
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install.packages}\NormalTok{(}\StringTok{"cheem"}\NormalTok{, }\AttributeTok{dependencies =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{library}\NormalTok{(}\StringTok{"cheem"}\NormalTok{)}
\FunctionTok{run\_app}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

To process your own data, you will need to use the \texttt{treeshap} package, which can be installed from GitHub:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{remotes}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{\textquotesingle{}ModelOriented/treeshap\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

and follow the examples provided with the package to compute the local explainers. XXX Add some information on what type of data object gets passed into cheem.

Alternatively, the cheem viewer shiny app can be directly accessed at \url{https://ebsmonash.shinyapps.io/cheem_initial/}.
